---
title: "Statistical Inference Course Project Part 2"
author: "Koji"
date: "2018/7/20"
output:
  pdf_document: default
  html_document: default
---

## Overview

Analyze the ToothGrowth data in the R datasets package.

1. Load the ToothGrowth data and perform some basic exploratory data analyses
2. Provide a basic summary of the data.
3. Use confidence intervals and/or hypothesis tests to compare tooth growth by supp and dose. (Only use the techniques from class, even if there's other approaches worth considering)
4. State your conclusions and the assumptions needed for your conclusions.


## Analysis

```{r, echo=FALSE}
library("ggplot2")
```

### ToothGrowth data
```{r}
# Load the ToothGrowth data
data("ToothGrowth")
str(ToothGrowth)
```

```{r}
?ToothGrowth
```
#### Description

The response is the length of odontoblasts (cells responsible for tooth growth) in 60 guinea pigs. Each animal received one of three dose levels of vitamin C (0.5, 1, and 2 mg/day) by one of two delivery methods, orange juice or ascorbic acid (a form of vitamin C and coded as VC).

### Basic summary
```{r}
summary(ToothGrowth)
```

```{r}
g <- ggplot(ToothGrowth, aes(x = factor(dose), y = len)) 
g <- g + geom_boxplot(aes(fill = factor(dose)))
g <- g + facet_grid(. ~ supp)
g <- g + ggtitle("Dose Amount vs Tooth Length")
g <- g + xlab("Dose Amount") + ylab("Length")
g
```

### Hypothesis Test


Now we will compare tooth growth by supplement using a t-test.

```{r}
t.test(len ~ supp, ToothGrowth)
```
The p-value of this test was 0.06.
Since the p-value is greater than 0.05 and the confidence interval of the test contains zero we can say that supplement types seems to have no impact on Tooth growth based on this test.

Now we’ll compare tooth growth by dose, looking at the different pairs of dose values.

```{r}
t.test(len ~ dose, ToothGrowth[ToothGrowth$dose %in% c(0.5, 1), ])
```

```{r}
t.test(len ~ dose, ToothGrowth[ToothGrowth$dose %in% c(1, 2), ])
```

As can be seen, the p-value of each test was essentially zero and the confidence interval of each test does not cross over zero.

Based on this result we can assume that the average tooth length increases with an inceasing dose, and therefore the null hypothesis can be rejected.

### Conclusions and Assumptions

In reviewing our t-test analysis from above, we can conclude that supplement type has no effect on tooth growth, and increasing the dose level leads to increased tooth growth..
